







\chapter*{Future Improvements}
\addcontentsline{toc}{chapter}{Future Improvements}

In this chapter, we outline future directions for the project and discuss upcoming enhancements and integrations.

\section*{Packaged Builds}
\addcontentsline{toc}{section}{Packaged Builds}

The goal of this project is to eventually provide packaged builds for easier deployment and distribution. Specifically, we aim to package the project for AUR (Arch User Repository) and as a PyPi (Python Package Index) library.

Some progress has already been made towards this goal; an early build is available for installation using the following command:
\[
\text{pip install -i https://test.pypi.org/simple/ game-genie}
\]
Unfortunately, pip support had to be temporarily halted until the application reaches a more stable and mature state.

\section*{Performance Evaluation}
\addcontentsline{toc}{section}{Performance Evaluation}

In this section, we assess the performance aspects of the application, focusing on runtime efficiency and optimization opportunities.

\subsection*{Speed Analysis}
\addcontentsline{toc}{subsection}{Speed Analysis}

To evaluate the speed of the application, various benchmarks and profiling techniques were employed. Preliminary tests indicate that the application performs adequately for its current scope. However, further optimization is planned to enhance performance in areas where execution time is critical.

\subsection*{Optimization Strategies}
\addcontentsline{toc}{subsection}{Optimization Strategies}

Several strategies for optimization have been identified, including algorithmic improvements, caching mechanisms, and parallel processing utilization. These strategies aim to reduce computational overhead and improve overall responsiveness.

\section*{Conclusion}
\addcontentsline{toc}{section}{Conclusion}

The future improvements outlined here pave the way for a more robust and efficient application. By focusing on packaged builds and performance enhancements, we aim to provide users with a smoother and more optimized experience.











% \chapter*{Future Improvements}
% \addcontentsline{toc}{chapter}{Future Improvements}
%   This has been a journey and after reading this paper you should have a view through the window of progress. There are still many to implement and properly integrate. There will be multiple update journals of this type posted on the following.

% \section*{Packaged builds}
%   The scope of this project is to one day make it as an AUR package and also a PyPi library.

%   Some work has already been made in this direction in the matter that one of the early builds is available by running 'pip install -i https://test.pypi.org/simple/ game-genie' in any terminal.
%   Unfortunately, I had to interrupt pip support for until application grows into a more stable and mature form.
